Optical Detection of Paramagnetic Defects in a CVD-grown Diamond

### 2021-02-26 Mes papiers/CR-CVD/SI/CVD_para_full_arxiv.tex
tutu

\section*{Appendix}
\subsection{Photoluminescence as a function of magnetic field in a HPHT sample}

@@

 \begin{figure}[htbp]
\centering
{\includegraphics[width=\linewidth]{sumi4_13C}}
\caption{NV$^-$ photoluminescence rate while scanning the magnetic field along the [100] crystalline direction. Here a HPHT sample was employed.}
\label{fig1SI}
\end{figure}

@@

\subsection{Magnetic field scan along the [111] direction}
\begin{figure}
\includegraphics[width=\linewidth]{scan_111_PL}
\caption{\textbf{a)} Plain blue line : Photoluminescence as a function of the magnetic field amplitude in the [111] crystalline direction. Dashed orange line : 4th order polynomial fit of the decreasing envelope. \textbf{b)} Subtraction of the previous signal by the envelope fit. The vertical dotted orange lines correspond to the expected cross-relaxations with VH$^-$ and the vertical dashed green lines to the expected cross-relaxations with WAR1.}\label{scan_PL}
\end{figure}

@@

%merlin.mbs apsrev4-1.bst 2010-07-25 4.21a (PWD, AO, DPC) hacked
%Control: key (0)
%Control: author (8) initials jnrlst
%Control: editor formatted (1) identically to author
%Control: production of article title (-1) disabled
%Control: page (0) single
%Control: year (1) truncated
%Control: production of eprint (0) enabled
\begin{thebibliography}{27}%
\makeatletter
\providecommand \@ifxundefined [1]{%
 \@ifx{#1\undefined}
}%
\providecommand \@ifnum [1]{%
 \ifnum #1\expandafter \@firstoftwo
 \else \expandafter \@secondoftwo
 \fi
}%
\providecommand \@ifx [1]{%
 \ifx #1\expandafter \@firstoftwo
 \else \expandafter \@secondoftwo
 \fi
}%
\providecommand \natexlab [1]{#1}%
\providecommand \enquote  [1]{``#1''}%
\providecommand \bibnamefont  [1]{#1}%
\providecommand \bibfnamefont [1]{#1}%
\providecommand \citenamefont [1]{#1}%
\providecommand \href@noop [0]{\@secondoftwo}%
\providecommand \href [0]{\begingroup \@sanitize@url \@href}%
\providecommand \@href[1]{\@@startlink{#1}\@@href}%
\providecommand \@@href[1]{\endgroup#1\@@endlink}%
\providecommand \@sanitize@url [0]{\catcode `\\12\catcode `\$12\catcode
  `\&12\catcode `\#12\catcode `\^12\catcode `\_12\catcode `\%12\relax}%
\providecommand \@@startlink[1]{}%
\providecommand \@@endlink[0]{}%
\providecommand \url  [0]{\begingroup\@sanitize@url \@url }%
\providecommand \@url [1]{\endgroup\@href {#1}{\urlprefix }}%
\providecommand \urlprefix  [0]{URL }%
\providecommand \Eprint [0]{\href }%
\providecommand \doibase [0]{http://dx.doi.org/}%
\providecommand \selectlanguage [0]{\@gobble}%
\providecommand \bibinfo  [0]{\@secondoftwo}%
\providecommand \bibfield  [0]{\@secondoftwo}%
\providecommand \translation [1]{[#1]}%
\providecommand \BibitemOpen [0]{}%
\providecommand \bibitemStop [0]{}%
\providecommand \bibitemNoStop [0]{.\EOS\space}%
\providecommand \EOS [0]{\spacefactor3000\relax}%
\providecommand \BibitemShut  [1]{\csname bibitem#1\endcsname}%
\let\auto@bib@innerbib\@empty
%</preamble>
\bibitem [{\citenamefont {Rondin}\ \emph {et~al.}(2014)\citenamefont {Rondin},
  \citenamefont {Tetienne}, \citenamefont {Hingant}, \citenamefont {Roch},
  \citenamefont {Maletinsky},\ and\ \citenamefont {Jacques}}]{Rondin_2014}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
  {Rondin}}, \bibinfo {author} {\bibfnamefont {J.-P.}\ \bibnamefont
  {Tetienne}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Hingant}},
  \bibinfo {author} {\bibfnamefont {J.-F.}\ \bibnamefont {Roch}}, \bibinfo
  {author} {\bibfnamefont {P.}~\bibnamefont {Maletinsky}}, \ and\ \bibinfo
  {author} {\bibfnamefont {V.}~\bibnamefont {Jacques}},\ }\href {\doibase
  10.1088/0034-4885/77/5/056503} {\bibfield  {journal} {\bibinfo  {journal}
  {Reports on Progress in Physics}\ }\textbf {\bibinfo {volume} {77}},\
  \bibinfo {pages} {056503} (\bibinfo {year} {2014})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Doherty}\ \emph {et~al.}(2013)\citenamefont
  {Doherty}, \citenamefont {Manson}, \citenamefont {Delaney}, \citenamefont
  {Jelezko}, \citenamefont {Wrachtrup},\ and\ \citenamefont
  {Hollenberg}}]{DOHERTY20131}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~W.}\ \bibnamefont
  {Doherty}}, \bibinfo {author} {\bibfnamefont {N.~B.}\ \bibnamefont {Manson}},
  \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Delaney}}, \bibinfo
  {author} {\bibfnamefont {F.}~\bibnamefont {Jelezko}}, \bibinfo {author}
  {\bibfnamefont {J.}~\bibnamefont {Wrachtrup}}, \ and\ \bibinfo {author}
  {\bibfnamefont {L.~C.}\ \bibnamefont {Hollenberg}},\ }\href {\doibase
  https://doi.org/10.1016/j.physrep.2013.02.001} {\bibfield  {journal}
  {\bibinfo  {journal} {Physics Reports}\ }\textbf {\bibinfo {volume} {528}},\
  \bibinfo {pages} {1 } (\bibinfo {year} {2013})},\ \bibinfo {note} {the
  nitrogen-vacancy colour centre in diamond}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Achard}\ \emph {et~al.}(2020)\citenamefont {Achard},
  \citenamefont {Jacques},\ and\ \citenamefont {Tallaire}}]{Achard}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
  {Achard}}, \bibinfo {author} {\bibfnamefont {V.}~\bibnamefont {Jacques}}, \
  and\ \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Tallaire}},\ }\href
  {\doibase 10.1088/1361-6463/ab81d1} {\bibfield  {journal} {\bibinfo
  {journal} {Journal of Physics D: Applied Physics}\ }\textbf {\bibinfo
  {volume} {53}},\ \bibinfo {pages} {313001} (\bibinfo {year}
  {2020})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Newton}(2007)}]{newton_epr_2007}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~E.}\ \bibnamefont
  {Newton}},\ }\href {\doibase 10.1002/chin.200747215} {\bibfield  {journal}
  {\bibinfo  {journal} {ChemInform}\ }\textbf {\bibinfo {volume} {38}}
  (\bibinfo {year} {2007}),\ 10.1002/chin.200747215}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Glover}\ \emph {et~al.}(2004)\citenamefont {Glover},
  \citenamefont {Newton}, \citenamefont {Martineau}, \citenamefont {Quinn},\
  and\ \citenamefont {Twitchen}}]{glover_hydrogen_2004}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
  {Glover}}, \bibinfo {author} {\bibfnamefont {M.~E.}\ \bibnamefont {Newton}},
  \bibinfo {author} {\bibfnamefont {P.~M.}\ \bibnamefont {Martineau}}, \bibinfo
  {author} {\bibfnamefont {S.}~\bibnamefont {Quinn}}, \ and\ \bibinfo {author}
  {\bibfnamefont {D.~J.}\ \bibnamefont {Twitchen}},\ }\href {\doibase
  10.1103/PhysRevLett.92.135502} {\bibfield  {journal} {\bibinfo  {journal}
  {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {92}},\ \bibinfo {pages}
  {135502} (\bibinfo {year} {2004})},\ \bibinfo {note} {publisher: American
  Physical Society}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Glover}\ \emph {et~al.}(2003)\citenamefont {Glover},
  \citenamefont {Newton}, \citenamefont {Martineau}, \citenamefont {Twitchen},\
  and\ \citenamefont {Baker}}]{glover_hydrogen_2003}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
  {Glover}}, \bibinfo {author} {\bibfnamefont {M.~E.}\ \bibnamefont {Newton}},
  \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Martineau}}, \bibinfo
  {author} {\bibfnamefont {D.~J.}\ \bibnamefont {Twitchen}}, \ and\ \bibinfo
  {author} {\bibfnamefont {J.~M.}\ \bibnamefont {Baker}},\ }\href {\doibase
  10.1103/PhysRevLett.90.185507} {\bibfield  {journal} {\bibinfo  {journal}
  {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {90}},\ \bibinfo {pages}
  {185507} (\bibinfo {year} {2003})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Yao}\ \emph {et~al.}(2012)\citenamefont {Yao},
  \citenamefont {Jiang}, \citenamefont {Gorshkov}, \citenamefont {Maurer},
  \citenamefont {Giedke}, \citenamefont {Cirac},\ and\ \citenamefont
  {Lukin}}]{Yao}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.~Y.}\ \bibnamefont
  {Yao}}, \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Jiang}}, \bibinfo
  {author} {\bibfnamefont {A.~V.}\ \bibnamefont {Gorshkov}}, \bibinfo {author}
  {\bibfnamefont {P.~C.}\ \bibnamefont {Maurer}}, \bibinfo {author}
  {\bibfnamefont {G.}~\bibnamefont {Giedke}}, \bibinfo {author} {\bibfnamefont
  {J.~I.}\ \bibnamefont {Cirac}}, \ and\ \bibinfo {author} {\bibfnamefont
  {M.~D.}\ \bibnamefont {Lukin}},\ }\href@noop {} {\bibfield  {journal}
  {\bibinfo  {journal} {Nature Communications}\ }\textbf {\bibinfo {volume}
  {3}},\ \bibinfo {pages} {800} (\bibinfo {year} {2012})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Cruddace}(2007)}]{cruddace2007magnetic}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
  {Cruddace}},\ }\emph {\bibinfo {title} {Magnetic resonance and optical
  studies of point defects in single crystal CVD diamond}},\ \href@noop {}
  {Ph.D. thesis},\ \bibinfo  {school} {University of Warwick} (\bibinfo {year}
  {2007})\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Epstein}\ \emph {et~al.}(2005)\citenamefont
  {Epstein}, \citenamefont {Mendoza}, \citenamefont {Kato},\ and\ \citenamefont
  {Awschalom}}]{Epstein}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.~J.}\ \bibnamefont
  {Epstein}}, \bibinfo {author} {\bibfnamefont {F.~M.}\ \bibnamefont
  {Mendoza}}, \bibinfo {author} {\bibfnamefont {Y.~K.}\ \bibnamefont {Kato}}, \
  and\ \bibinfo {author} {\bibfnamefont {D.~D.}\ \bibnamefont {Awschalom}},\
  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Nature Physics}\
  }\textbf {\bibinfo {volume} {1}},\ \bibinfo {pages} {94} (\bibinfo {year}
  {2005})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Wang}\ \emph {et~al.}(2014)\citenamefont {Wang},
  \citenamefont {Shin}, \citenamefont {Seltzer}, \citenamefont {Avalos},
  \citenamefont {Pines},\ and\ \citenamefont {Bajaj}}]{Wang}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.-J.}\ \bibnamefont
  {Wang}}, \bibinfo {author} {\bibfnamefont {C.~S.}\ \bibnamefont {Shin}},
  \bibinfo {author} {\bibfnamefont {S.~J.}\ \bibnamefont {Seltzer}}, \bibinfo
  {author} {\bibfnamefont {C.~E.}\ \bibnamefont {Avalos}}, \bibinfo {author}
  {\bibfnamefont {A.}~\bibnamefont {Pines}}, \ and\ \bibinfo {author}
  {\bibfnamefont {V.~S.}\ \bibnamefont {Bajaj}},\ }\href@noop {} {\bibfield
  {journal} {\bibinfo  {journal} {Nature Communications}\ }\textbf {\bibinfo
  {volume} {5}},\ \bibinfo {pages} {4135} (\bibinfo {year} {2014})}\BibitemShut
  {NoStop}%
\bibitem [{\citenamefont {Armstrong}\ \emph {et~al.}(2010)\citenamefont
  {Armstrong}, \citenamefont {Rogers}, \citenamefont {McMurtrie},\ and\
  \citenamefont {Manson}}]{armstrong_nvnv_2010}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
  {Armstrong}}, \bibinfo {author} {\bibfnamefont {L.~J.}\ \bibnamefont
  {Rogers}}, \bibinfo {author} {\bibfnamefont {R.~L.}\ \bibnamefont
  {McMurtrie}}, \ and\ \bibinfo {author} {\bibfnamefont {N.~B.}\ \bibnamefont
  {Manson}},\ }\href {\doibase 10.1016/j.phpro.2010.01.223} {\bibfield
  {journal} {\bibinfo  {journal} {Physics Procedia}\ }\textbf {\bibinfo
  {volume} {3}},\ \bibinfo {pages} {1569} (\bibinfo {year} {2010})},\ \bibinfo
  {note} {number: 4}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Hall}\ \emph {et~al.}(2016)\citenamefont {Hall},
  \citenamefont {Kehayias}, \citenamefont {Simpson}, \citenamefont {Jarmola},
  \citenamefont {Stacey}, \citenamefont {Budker},\ and\ \citenamefont
  {Hollenberg}}]{Hall}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.~T.}\ \bibnamefont
  {Hall}}, \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Kehayias}},
  \bibinfo {author} {\bibfnamefont {D.~A.}\ \bibnamefont {Simpson}}, \bibinfo
  {author} {\bibfnamefont {A.}~\bibnamefont {Jarmola}}, \bibinfo {author}
  {\bibfnamefont {A.}~\bibnamefont {Stacey}}, \bibinfo {author} {\bibfnamefont
  {D.}~\bibnamefont {Budker}}, \ and\ \bibinfo {author} {\bibfnamefont
  {L.~C.~L.}\ \bibnamefont {Hollenberg}},\ }\href@noop {} {\bibfield  {journal}
  {\bibinfo  {journal} {Nature Communications}\ }\textbf {\bibinfo {volume}
  {7}},\ \bibinfo {pages} {10211} (\bibinfo {year} {2016})}\BibitemShut
  {NoStop}%
\bibitem [{\citenamefont {Wickenbrock}\ \emph {et~al.}(2016)\citenamefont
  {Wickenbrock}, \citenamefont {Zheng}, \citenamefont {Bougas}, \citenamefont
  {Leefer}, \citenamefont {Afach}, \citenamefont {Jarmola}, \citenamefont
  {Acosta},\ and\ \citenamefont {Budker}}]{Wickenbrock}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
  {Wickenbrock}}, \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Zheng}},
  \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Bougas}}, \bibinfo
  {author} {\bibfnamefont {N.}~\bibnamefont {Leefer}}, \bibinfo {author}
  {\bibfnamefont {S.}~\bibnamefont {Afach}}, \bibinfo {author} {\bibfnamefont
  {A.}~\bibnamefont {Jarmola}}, \bibinfo {author} {\bibfnamefont {V.~M.}\
  \bibnamefont {Acosta}}, \ and\ \bibinfo {author} {\bibfnamefont
  {D.}~\bibnamefont {Budker}},\ }\href {\doibase 10.1063/1.4960171} {\bibfield
  {journal} {\bibinfo  {journal} {Applied Physics Letters}\ }\textbf {\bibinfo
  {volume} {109}},\ \bibinfo {pages} {053505} (\bibinfo {year} {2016})},\
  \Eprint {http://arxiv.org/abs/https://doi.org/10.1063/1.4960171}
  {https://doi.org/10.1063/1.4960171} \BibitemShut {NoStop}%
\bibitem [{\citenamefont {Alfasi}\ \emph {et~al.}(2019)\citenamefont {Alfasi},
  \citenamefont {Masis}, \citenamefont {Shtempluck},\ and\ \citenamefont
  {Buks}}]{Alfasi}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
  {Alfasi}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Masis}},
  \bibinfo {author} {\bibfnamefont {O.}~\bibnamefont {Shtempluck}}, \ and\
  \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {Buks}},\ }\href {\doibase
  10.1103/PhysRevB.99.214111} {\bibfield  {journal} {\bibinfo  {journal} {Phys.
  Rev. B}\ }\textbf {\bibinfo {volume} {99}},\ \bibinfo {pages} {214111}
  (\bibinfo {year} {2019})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {{Edmonds}}\ \emph {et~al.}(2020)\citenamefont
  {{Edmonds}}, \citenamefont {{Hart}}, \citenamefont {{Turner}}, \citenamefont
  {{Colard}}, \citenamefont {{Schloss}}, \citenamefont {{Olsson}},
  \citenamefont {{Trubko}}, \citenamefont {{Markham}}, \citenamefont
  {{Rathmill}}, \citenamefont {{Horne-Smith}}, \citenamefont {{Lew}},
  \citenamefont {{Manickam}}, \citenamefont {{Bruce}}, \citenamefont {{Kaup}},
  \citenamefont {{Russo}}, \citenamefont {{DiMario}}, \citenamefont {{South}},
  \citenamefont {{Hansen}}, \citenamefont {{Twitchen}},\ and\ \citenamefont
  {{Walsworth}}}]{Edmonds}%
  \BibitemOpen

>>>>

\section*{Appendix}
\subsection{Photoluminescence as a function of the magnetic field for a HPHT sample}

@@

 \begin{figure}[htbp]
\centering
{\includegraphics[width=\linewidth]{sumi4_13C.eps}}
\caption{NV$^-$ photoluminescence rate while scanning the magnetic field along the [100] crystalline direction. Here a HPHT sample was employed.}
\label{fig1SI}
\end{figure}

@@

\subsection{Scan in the [111] direction}
\begin{figure}
\includegraphics[width=\linewidth]{scan_111_PL}
\caption{\textbf{a)} Plain blue line : Photoluminescence as a function of the magnetic field amplitude in the [111] crystalline direction. Dashed orange line : 4th order polynomial fit of the decreasing envelope. \textbf{b)} Subtraction of the previous signal by the envelope fit. The vertical dotted orange lines correspond to the expected cross-relaxations with VH$^-$ and the vertical dashed green lines to the expected cross-relaxations with WAR1.}\label{scan_PL}
\end{figure}

@@

\subsection{Fitting of the cross-relaxation scans}
\begin{figure}
\includegraphics[scale=0.5]{Gauss_vs_Lor_VH}
\caption{Zoom-in on the VH$^-$ cross-relaxation line from Fig.3 of the main text with Gaussian (orange,plain line) and Lorentzian (red, dashed line) fit}
\label{Gauss_vs_Lor}
\end{figure}
In order to extract quantitative information from Fig.3 of the main text, we had ta apply two distinct fits to the raw data : first a polynomial fit to subtract the slowly decaying PL due to sate-mixing, then a Lorentzian fit on the VH$^-$ and WAR1 resonance lines to measure the central position, width and amplitude of the lines.

For the subtracting fit, we chose a polynomial fit because numerical solving of the transverse-field dependent spin depolarization could not properly fit our results. We had to use up a 4th order polynomial in order to obtain a tight fit to the data. Higher order polynomials did not significantly change the fitting envelope.

The second and third peaks were fitted better on their wings by a Gaussian than by a Lorentzian lineshape, as can be seen in Fig.\ref{Gauss_vs_Lor} where the Gaussian fit yields a $R^2=0.983$ greater than the $R^2=0.974$ from the Lorentzian fit. This is coherent with the fact that the inhomogeneous broadening of the various spin species dominates the coupling strength between the spins.

\subsection{Sample fabrication details}
The main CVD sample of this study is presented in thorough details in \citep{TALLAIRE2020421}. It is a thick (100) oriented diamond grown in-house by CVD with an initial concentration [N]$\approx$25~ppm and separated from its HPHT substrate. It was electron irradiated at 10MeV and a fluence of $2\cdot 10^{18}$~cm$^{-2}$ and in situ annealed at 900°C during irradiation to give a final concentration [NV]$\approx$4.6~ppm.

The HPHT sample used in Sec.I of the supplementary material is a thick (111)-oriented diamond from Sumitomo and was electron irradiated at an energy of 2 MeV and a fluence of $7\cdot 10^{18}$~cm$^{-2}$. It was then annealed in vacuum for 2h at 950°C.

We also tried the same experiment on similar HPHT samples with a fluence ranging from $4\cdot 10^{18}$~cm$^{-2}$ to $1.5\cdot 10^{18}$~cm$^{-2}$, as well as on several heavily doped 15 $\mu$m diamonds bought from Adamas Nanotechnologies, and all the HPHT sample showed a feature at $\sim$20~G, but none of them showed any feature at 56 or 125~G.

\begin{thebibliography}{10}

\bibitem{Achard}
J~Achard, V~Jacques, and A~Tallaire.
\newblock Chemical vapour deposition diamond single crystals with
  nitrogen-vacancy centres: a review of material synthesis and technology for
  quantum sensing applications.
\newblock {\em Journal of Physics D: Applied Physics}, 53(31):313001, may 2020.

\bibitem{akhmedzhanov_microwave-free_2017}
Rinat Akhmedzhanov, Lev Gushchin, Nikolay Nizov, Vladimir Nizov, Dmitry
  Sobgayda, Ilya Zelensky, and Philip Hemmer.
\newblock Microwave-free magnetometry based on cross-relaxation resonances in
  diamond nitrogen-vacancy centers.
\newblock {\em Phys. Rev. A}, 96(1):013806, July 2017.
\newblock Number: 1.

\bibitem{akhmedzhanov_magnetometry_2019}
Rinat Akhmedzhanov, Lev Gushchin, Nikolay Nizov, Vladimir Nizov, Dmitry
  Sobgayda, Ilya Zelensky, and Philip Hemmer.
\newblock Magnetometry by cross-relaxation-resonance detection in ensembles of
  nitrogen-vacancy centers.
\newblock {\em Phys. Rev. A}, 100(4):043844, October 2019.
\newblock Number: 4.

\bibitem{Alfasi}
Nir Alfasi, Sergei Masis, Oleg Shtempluck, and Eyal Buks.
\newblock Detection of paramagnetic defects in diamond using off-resonance
  excitation of nv centers.
\newblock {\em Phys. Rev. B}, 99:214111, Jun 2019.

\bibitem{alfasi2019detection}
Nir Alfasi, Sergei Masis, Oleg Shtempluck, and Eyal Buks.
\newblock Detection of paramagnetic defects in diamond using off-resonance
  excitation of nv centers.
\newblock {\em Physical Review B}, 99(21):214111, 2019.

\bibitem{armstrong_nvnv_2010}
Seiji Armstrong, Lachlan~J. Rogers, Roger~L. McMurtrie, and Neil~B. Manson.
\newblock {NV}–{NV} electron–electron spin and {NV}–{NS} electron —
  electron and electron-nuclear spin interaction in diamond.
\newblock {\em Physics Procedia}, 3(4):1569--1575, February 2010.
\newblock Number: 4.

\bibitem{Ashfold}
Michael N.~R. Ashfold, Jonathan~P. Goss, Ben~L. Green, Paul~W. May, Mark~E.
  Newton, and Chloe~V. Peaker.
\newblock Nitrogen in diamond.
\newblock {\em Chemical Reviews}, 120(12):5745--5794, 06 2020.

\bibitem{choi_depolarization_2017}
Joonhee Choi, Soonwon Choi, Georg Kucsko, Peter~C. Maurer, Brendan~J. Shields,
  Hitoshi Sumiya, Shinobu Onoda, Junichi Isoya, Eugene Demler, Fedor Jelezko,
  Norman~Y. Yao, and Mikhail~D. Lukin.
\newblock Depolarization {Dynamics} in a {Strongly} {Interacting}
  {Solid}-{State} {Spin} {Ensemble}.
\newblock {\em Phys. Rev. Lett.}, 118(9):093601, March 2017.
\newblock Number: 9.

\bibitem{cruddace2007magnetic}
Robin Cruddace.
\newblock {\em Magnetic resonance and optical studies of point defects in
  single crystal CVD diamond}.
\newblock PhD thesis, University of Warwick, 2007.

\bibitem{DOHERTY20131}
Marcus~W. Doherty, Neil~B. Manson, Paul Delaney, Fedor Jelezko, Jörg
  Wrachtrup, and Lloyd~C.L. Hollenberg.
\newblock The nitrogen-vacancy colour centre in diamond.
\newblock {\em Physics Reports}, 528(1):1 -- 45, 2013.
\newblock The nitrogen-vacancy colour centre in diamond.

\bibitem{Edmonds}
Andrew~M. {Edmonds}, Connor~A. {Hart}, Matthew~J. {Turner}, Pierre-Olivier
  {Colard}, Jennifer~M. {Schloss}, Kevin {Olsson}, Raisa {Trubko}, Matthew~L.
  {Markham}, Adam {Rathmill}, Ben {Horne-Smith}, Wilbur {Lew}, Arul {Manickam},
  Scott {Bruce}, Peter~G. {Kaup}, Jon~C. {Russo}, Michael~J. {DiMario},
  Joseph~T. {South}, Jay~T. {Hansen}, Daniel~J. {Twitchen}, and Ronald~L.
  {Walsworth}.
\newblock {Generation of nitrogen-vacancy ensembles in diamond for quantum
  sensors: Optimization and scalability of CVD processes}.
\newblock {\em arXiv e-prints}, page arXiv:2004.01746, April 2020.

\bibitem{Epstein}
R.~J. Epstein, F.~M. Mendoza, Y.~K. Kato, and D.~D. Awschalom.
\newblock Anisotropic interactions of a single spin and dark-spin spectroscopy
  in diamond.
\newblock {\em Nature Physics}, 1(2):94--98, 2005.

\bibitem{glover_hydrogen_2003}
Claire Glover, M.~E. Newton, P.~Martineau, D.~J. Twitchen, and J.~M. Baker.
\newblock Hydrogen {Incorporation} in {Diamond}: {The}
  {Nitrogen}-{Vacancy}-{Hydrogen} {Complex}.
\newblock {\em Phys. Rev. Lett.}, 90(18):185507, May 2003.

\bibitem{glover_hydrogen_2004}
Claire Glover, M.~E. Newton, P.~M. Martineau, Samantha Quinn, and D.~J.
  Twitchen.
\newblock Hydrogen {Incorporation} in {Diamond}: {The} {Vacancy}-{Hydrogen}
  {Complex}.
\newblock {\em Phys. Rev. Lett.}, 92(13):135502, March 2004.
\newblock Publisher: American Physical Society.

\bibitem{Hall}
L.~T. Hall, P.~Kehayias, D.~A. Simpson, A.~Jarmola, A.~Stacey, D.~Budker, and
  L.~C.~L. Hollenberg.
\newblock Detection of nanoscale electron spin resonance spectra demonstrated
  using nitrogen-vacancy centre probes in diamond.
\newblock {\em Nature Communications}, 7(1):10211, 2016.

\bibitem{holliday_optical_1989}
K~Holliday, N~B Manson, M~Glasbeek, and E~van Oort.
\newblock Optical hole-bleaching by level anti-crossing and cross relaxation in
  the {N}-{V} centre in diamond.
\newblock {\em J. Phys.: Condens. Matter}, 1(39):7093--7102, October 1989.
\newblock Number: 39.

\bibitem{jarmola_longitudinal_2015}
A.~Jarmola, A.~Berzins, J.~Smits, K.~Smits, J.~Prikulis, F.~Gahbauer,
  R.~Ferber, D.~Erts, M.~Auzinsh, and D.~Budker.
\newblock Longitudinal spin-relaxation in nitrogen-vacancy centers in electron
  irradiated diamond.
\newblock {\em Appl. Phys. Lett.}, 107(24):242403, December 2015.
\newblock Number: 24.

\bibitem{jiang2018estimation}
Feng-Jian Jiang, Jian-Feng Ye, Zheng Jiao, Zhi-Yong Huang, and Hai-Jiang Lv.
\newblock Estimation of vector static magnetic field by a nitrogen-vacancy
  center with a single first-shell 13c nuclear (nv--13c) spin in diamond.
\newblock {\em Chinese Physics B}, 27(5):057601, 2018.

\bibitem{kamp2018continuous}
EJ~Kamp, B~Carvajal, and N~Samarth.
\newblock Continuous wave protocol for simultaneous polarization and optical
  detection of p1-center electron spin resonance.
\newblock {\em Physical Review B}, 97(4):045204, 2018.

\bibitem{lazda2020cross}
Reinis Lazda, Laima Busaite, Andris Berzins, Janis Smits, Marcis Auzinsh,
  Dmitry Budker, Ruvin Ferber, and Florian Gahbauer.
\newblock Cross-relaxation studies with optically detected magnetic resonances
  in nitrogen-vacancy centers in diamond in an external magnetic field.
\newblock {\em arXiv preprint arXiv:2007.00473}, 2020.

\bibitem{MINDARAVA2020182}
Yuliya Mindarava, Rémi Blinder, Christian Laube, Wolfgang Knolle, Bernd Abel,
  Christian Jentgens, Junichi Isoya, Jochen Scheuer, Johannes Lang, Ilai
  Schwartz, Boris Naydenov, and Fedor Jelezko.
\newblock Efficient conversion of nitrogen to nitrogen-vacancy centers in
  diamond particles with high-temperature electron irradiation.
\newblock {\em Carbon}, 170:182 -- 190, 2020.

\bibitem{newton_epr_2007}
M.~E. Newton.
\newblock {EPR}, {ENDOR} and {EPR} {Imaging} of {Defects} in {Diamond}.
\newblock {\em ChemInform}, 38(47), November 2007.

\bibitem{Rondin_2014}
L~Rondin, J-P Tetienne, T~Hingant, J-F Roch, P~Maletinsky, and V~Jacques.
\newblock Magnetometry with nitrogen-vacancy defects in diamond.
\newblock {\em Reports on Progress in Physics}, 77(5):056503, may 2014.

\bibitem{simanovskaia_sidebands_2013}
Maria Simanovskaia, Kasper Jensen, Andrey Jarmola, Kurt Aulenbacher, Neil
  Manson, and Dmitry Budker.
\newblock Sidebands in optically detected magnetic resonance signals of
  nitrogen vacancy centers in diamond.
\newblock {\em Phys. Rev. B}, 87(22):224106, June 2013.

\bibitem{smeltzer201113c}
Benjamin Smeltzer, Lilian Childress, and Adam Gali.
\newblock 13c hyperfine interactions in the nitrogen-vacancy centre in diamond.
\newblock {\em New Journal of Physics}, 13(2):025021, 2011.

\bibitem{TALLAIRE2020421}
Alexandre Tallaire, Ovidiu Brinza, Paul Huillery, Tom Delord, Clément
  Pellet-Mary, Robert Staacke, Bernd Abel, Sébastien Pezzagna, Jan Meijer,
  Nadia Touati, Laurent Binet, Alban Ferrier, Philippe Goldner, Gabriel Hetet,
  and Jocelyn Achard.
\newblock High nv density in a pink cvd diamond grown with n2o addition.
\newblock {\em Carbon}, 170:421 -- 429, 2020.

\bibitem{van_oort_optically_1991}
E.~van Oort and M.~Glasbeek.
\newblock Optically detected adiabatic fast passage and cross-relaxation of the
  {N}-{V} center in diamond.
\newblock {\em Appl Magn Reson}, 2(2):291--300, June 1991.
\newblock Number: 2.

\bibitem{van_oort_cross-relaxation_1989}
Eric van Oort and Max Glasbeek.
\newblock Cross-relaxation dynamics of optically excited \textit{{N}} -
  \textit{{V}} centers in diamond.
\newblock {\em Phys. Rev. B}, 40(10):6509--6517, October 1989.
\newblock Number: 10.

\bibitem{Wang}
Hai-Jing Wang, Chang~S. Shin, Scott~J. Seltzer, Claudia~E. Avalos, Alexander
  Pines, and Vikram~S. Bajaj.
\newblock Optically detected cross-relaxation spectroscopy of electron spins in
  diamond.
\newblock {\em Nature Communications}, 5(1):4135, 2014.

\bibitem{Wickenbrock}
Arne Wickenbrock, Huijie Zheng, Lykourgos Bougas, Nathan Leefer, Samer Afach,
  Andrey Jarmola, Victor~M. Acosta, and Dmitry Budker.
\newblock Microwave-free magnetometry with nitrogen-vacancy centers in diamond.
\newblock {\em Applied Physics Letters}, 109(5):053505, 2016.

\bibitem{Yao}
N.~Y. Yao, L.~Jiang, A.~V. Gorshkov, P.~C. Maurer, G.~Giedke, J.~I. Cirac, and
  M.~D. Lukin.
\newblock Scalable architecture for a room temperature solid-state quantum
  information processor.
\newblock {\em Nature Communications}, 3(1):800, 2012.

\bibitem{alvarez_local_2015}
Gonzalo~A. Álvarez, Christian~O. Bretschneider, Ran Fischer, Paz London, Hisao
  Kanda, Shinobu Onoda, Junichi Isoya, David Gershoni, and Lucio Frydman.
\newblock Local and bulk {13C} hyperpolarization in nitrogen-vacancy-centred
  diamonds at variable fields and orientations.
\newblock {\em Nat Commun}, 6(1):8456, December 2015.

\end{thebibliography}
